---
title: "YSM_FinalReport_clinicalexam"
author: "Gema Vidal_7526"
date: "10/6/2020"
output: word_document
---


```{r}
library("tidyverse")
library("plyr")
library("dplyr")
library("MASS")
library("car")
library("foreign")
library("psych")
library("stats")
library("Matrix")
library("lme4")
library("lattice")
#library("gmodels") # for CrossTable
#library("irr")
library("vcd")
library("lsmeans") # for contrasts
library('GGally')
library("tableone")
```



```{r}
setwd("/Users/gemavidal/Box Sync/Vet/Projects and Papers/2020 YSM USAID Final Report")
df = read.csv("df_clinicalexam_cleaned.csv", stringsAsFactors = TRUE)
```


```{r}
str(df)
```


```{r}
levels(df$Species)[levels(df$Species) == ""] <- NA
levels(df$abdomen_pingsounds)[levels(df$abdomen_pingsounds) == ""] <- NA
levels(df$abdomenauscultation_notes)[levels(df$abdomenauscultation_notes) == ""] <- NA
levels(df$abdomenauscultation_notes)[levels(df$abdomenauscultation_notes) == " "] <- NA
levels(df$attitude)[levels(df$attitude) == ""] <- NA
levels(df$coccidia_species_result)[levels(df$coccidia_species_result) == ""] <- NA
levels(df$coughing)[levels(df$coughing) == ""] <- NA
levels(df$crackles)[levels(df$crackles) == ""] <- NA
levels(df$generalnotes)[levels(df$generalnotes) == ""] <- NA
levels(df$jointsexam)[levels(df$jointsexam) == ""] <- NA
levels(df$jointsexam_notes)[levels(df$jointsexam_notes) == ""] <- NA
levels(df$navel)[levels(df$navel) == ""] <- NA
levels(df$navelexam_notes)[levels(df$navelexam_notes) == ""] <- NA
levels(df$parasitology_other_result)[levels(df$parasitology_other_result) == ""] <- NA
levels(df$result_IBR)[levels(df$result_IBR) == ""] <- NA
levels(df$result_RID)[levels(df$result_RID) == ""] <- NA
levels(df$IgG_Status)[levels(df$IgG_Status) == ""] <- NA
levels(df$result_IgG)[levels(df$result_IgG) == ""] <- NA
levels(df$student)[levels(df$student) == ""] <- NA
levels(df$test_kit)[levels(df$test_kit) == ""] <- NA
levels(df$thoracicauscultation_notes)[levels(df$thoracicauscultation_notes) == ""] <- NA
levels(df$feces_blood)[levels(df$feces_blood) == ""] <- NA
levels(df$typeofdiarrhea)[levels(df$typeofdiarrhea) == ""] <- NA
levels(df$typeofdiarrhea_nuru_chalachew)[levels(df$typeofdiarrhea_nuru_chalachew) == ""] <- NA
levels(df$wheezes)[levels(df$wheezes) == ""] <- NA
```


```{r}
df$age_weeks_catg <- cut(df$age_weeks, c(0, 1, 2, 4, 8, 24, 100))
df$parity_catg <- cut(df$parity, c(0, 1, 2, 3, 4, 16))
df$dam_ageparturition_catg <- cut(df$dam_ageparturition_years, c(0, 5, 7, 8, 16))
```



Clinical Exam
-------------

Select a subset of data that contains clinical exam data only
```{r}
df_exam <- subset(df, ((!is.na(df$BCS)) | 
                      (!is.na(df$attitude)) |
                      (!is.na(df$cough_score)) |
                        (!is.na(df$ear_score)) |
                        (!is.na(df$eye_score)) |
                        (!is.na(df$nasaldischarge_score)) |
                        (!is.na(df$rectal_temp)) |
                        (!is.na(df$rectal_temp_score)) |
                        (!is.na(df$fecal_score)) |
                        (!is.na(df$coughing)) |
                        (!is.na(df$crackles)) |
                        (!is.na(df$increased_respiratoryeffort)) |
                        (!is.na(df$jointsexam)) |
                        (!is.na(df$navel)) |
                        (!is.na(df$heart_rate_perminute)) |
                        (!is.na(df$respiratory_rate_perminute))), 
                  select = c("BCS","attitude",
                             "cough_score","ear_score",
                             "eye_score","nasaldischarge_score",
                             "rectal_temp_score","fecal_score",
                             "coughing","crackles",
                             "increased_respiratoryeffort","jointsexam",
                             "navel","heart_rate_perminute",
                             "respiratory_rate_perminute",
                             "result_IgG","Species","district","parity","parity_catg",
                             "prod_system","age_weeks","age_weeks_catg"))
```


Drop unused levels
```{r}
df_exam$BCS <- factor(df_exam$BCS)
df_exam$attitude <- factor(df_exam$attitude)
df_exam$cough_score <- factor(df_exam$cough_score)
df_exam$ear_score <- factor(df_exam$ear_score)
df_exam$eye_score <- factor(df_exam$eye_score)

df_exam$nasaldischarge_score <- factor(df_exam$nasaldischarge_score)
df_exam$rectal_temp_score <- factor(df_exam$rectal_temp_score)
df_exam$fecal_score <- factor(df_exam$fecal_score)
df_exam$coughing <- factor(df_exam$coughing)
df_exam$crackles <- factor(df_exam$crackles)

df_exam$increased_respiratoryeffort <- factor(df_exam$increased_respiratoryeffort)
df_exam$jointsexam <- factor(df_exam$jointsexam)
df_exam$navel <- factor(df_exam$navel)
df_exam$result_IgG <- factor(df_exam$result_IgG)
df_exam$Species <- factor(df_exam$Species)

df_exam$district <- factor(df_exam$district)
df_exam$parity_catg <- factor(df_exam$parity_catg)
df_exam$prod_system <- factor(df_exam$prod_system)
df_exam$age_weeks_catg <- factor(df_exam$age_weeks_catg)
```


```{r}
str(df_exam$nasaldischarge_score)
```



```{r}
df_exam$age_weeks_catg <- cut(df_exam$age_weeks, c(0, 4, 12, 100))
df_exam$cough_score_catg <- revalue(df_exam$cough_score, c("0"="<1", "1"="<1",
                                                           "2"="2+", "3"="2+"))
df_exam$nasaldischarge_score_catg <- revalue(df_exam$nasaldischarge_score, c("0"="<1", "1"="<1",
                                                                             "2"="2+", "3"="2+"))
df_exam$ear_score_catg <- revalue(df_exam$ear_score, c("0"="<1", "1"="<1",
                                                       "2"="2+", "3"="2+"))

df_exam$eye_score_catg <- revalue(df_exam$eye_score, c("0"="<1", "1"="<1",
                                                       "2"="2+", "3"="2+"))

df_exam$rectal_temp_catg <- revalue(df_exam$rectal_temp_score, c("0"="<1", "1"="<1",
                                                                 "2"="2+", "3"="2+"))

df_exam$fecal_score_catg <- revalue(df_exam$fecal_score, c("0"="<1", "1"="<1",
                                                           "2"="2+", "3"="2+"))
```

```{r}
df_exam$BCS_catg <- revalue(df_exam$BCS, c("1"="1", "2"="2", "3"="3", "4"="4+", "5"="4+"))
```



Respiratory Symptoms
```{r}
df_exam_resp <- df_exam[ which(df_exam$prod_system != "Mixed-crop"), ]

tableOne_resp <- CreateTableOne(vars = c("cough_score_catg","nasaldischarge_score_catg",
                                         "coughing","crackles",
                                         "increased_respiratoryeffort"), 
                                strata = c("prod_system"), 
                                data= df_exam_resp, 
                                factorVars = c("prod_system","age_weeks_catg"))

tableOne_resp
```


```{r}
tableOne_resp <- CreateTableOne(vars = c("cough_score_catg","nasaldischarge_score_catg",
                                         "coughing","crackles",
                                         "increased_respiratoryeffort"), 
                                strata = c("prod_system","age_weeks_catg"), 
                                data= df_exam_resp, 
                                factorVars = c("prod_system","age_weeks_catg"))

tableOne_resp
```

```{r}
tableOne_resp <- CreateTableOne(vars = c("cough_score_catg","nasaldischarge_score_catg",
                                         "coughing","crackles",
                                         "increased_respiratoryeffort"), 
                                strata = c("age_weeks_catg"), 
                                data= df_exam_resp, 
                                factorVars = c("prod_system","age_weeks_catg"))

tableOne_resp
```



```{r}
tableOne_general <- CreateTableOne(vars = c("BCS_catg","cough_score_catg",
                                            "ear_score_catg","eye_score_catg",
                                            "nasaldischarge_score_catg","rectal_temp_catg",
                                            "fecal_score_catg"), 
                                   strata = c("prod_system"), 
                                   data= df_exam, 
                                   factorVars = c("prod_system","age_weeks_catg"))

tableOne_general
```
I did not use cough score, ear score, eye score, or nasal discharge score any further because of data quality issues.


Using the variables I can use
```{r}
tableOne_general <- CreateTableOne(vars = c("BCS_catg",
                                            "rectal_temp_catg",
                                            "fecal_score_catg"), 
                                   strata = c("prod_system"), 
                                   data= df_exam, 
                                   factorVars = c("prod_system","age_weeks_catg"))

tableOne_general
```

What the association between fecal score and BCS? 
```{r}
tableOne_general <- CreateTableOne(vars = c("BCS_catg"), 
                                   strata = c("fecal_score_catg"), 
                                   data= df_exam, 
                                   factorVars = c("prod_system","age_weeks_catg","rectal_temp_catg","fecal_score_catg"))

tableOne_general
```


Is also age related with BCS? or maternal malnutrition? are stunted calves being less healthy?
```{r}
tableOne_general <- CreateTableOne(vars = c("BCS_catg"), 
                                   strata = c("age_weeks_catg","fecal_score_catg"), 
                                   data= df_exam, 
                                   factorVars = c("prod_system","age_weeks_catg","rectal_temp_catg","fecal_score_catg"))

tableOne_general
```


Since we are interested in what is the age distribution and BCS distribution among those with diarrhea, I will take a subset for fecal score > 2+ and then I'll do the table again
```{r}
df_exam_diarrhea <- df_exam[df_exam$fecal_score_catg == "2+", ]
df_exam_diarrhea$fecal_score_catg <- factor(df_exam_diarrhea$fecal_score_catg)
```

```{r}
tableOne_general <- CreateTableOne(vars = c("BCS_catg"), 
                                   strata = c("age_weeks_catg"), 
                                   data= df_exam_diarrhea, 
                                   factorVars = c("prod_system","age_weeks_catg","rectal_temp_catg"))

tableOne_general
```






```{r}
tableOne_general <- CreateTableOne(vars = c("BCS_catg"), 
                                   strata = c("prod_system"), 
                                   data= df_exam, 
                                   factorVars = c("prod_system","age_weeks_catg","rectal_temp_catg","fecal_score_catg"))

tableOne_general
```










