---
title: "YSM_FinalReport_animal"
author: "Gema Vidal_7526"
date: "10/7/2020"
output: word_document
---


```{r}
library("tidyverse")
library("plyr")
library("dplyr")
library("MASS")
library("car")
library("foreign")
library("psych")
library("stats")
library("Matrix")
library("lme4")
library("lattice")
#library("gmodels") # for CrossTable
#library("irr")
library("vcd")
library("lsmeans") # for contrasts
library('GGally')
library("tableone")
```


```{r}
setwd("/Users/gemavidal/Box Sync/Vet/Projects and Papers/2020 YSM USAID Final Report")
df = read.csv("df_animal_cleaned.csv", stringsAsFactors = TRUE)
```


```{r}
str(df)
```


```{r}
levels(df$age_units)[levels(df$age_units) == ""] <- NA
levels(df$birth_witness)[levels(df$birth_witness) == ""] <- NA
levels(df$birthlocation)[levels(df$birthlocation) == ""] <- NA
levels(df$breed)[levels(df$breed) == ""] <- NA
levels(df$breed_name)[levels(df$breed_name) == ""] <- NA
levels(df$calf_bcs)[levels(df$calf_bcs) == ""] <- NA
levels(df$sex)[levels(df$sex) == ""] <- NA
levels(df$sire)[levels(df$sire) == ""] <- NA
levels(df$timeofbirth)[levels(df$timeofbirth) == ""] <- NA
levels(df$typedelivery)[levels(df$typedelivery) == ""] <- NA
levels(df$weaned)[levels(df$weaned) == ""] <- NA
levels(df$weaned_agemonths)[levels(df$weaned_agemonths) == ""] <- NA
```


Drop unused levels
```{r}
df[c(4:16)] <- lapply(df[c(4:16)], factor)
```


```{r}
df$birthlocation <- revalue(df$birthlocation, c("Calving pen"="In barn", "In barn"="In barn",
                                                "Outside"="Outside", "Same cow barn"="In barn"))
```




```{r}
tableOne_anim <- CreateTableOne(vars = c("birth_witness","birthlocation",
                                         "breed","breed_name",
                                         "calf_bcs", "sire", "timeofbirth", "typedelivery"), 
                                strata = c("prod_system"), 
                                data= df, 
                                factorVars = c("prod_system"))

tableOne_anim
```


```{r}
tableOne_anim <- CreateTableOne(vars = c("birth_witness",
                                         "breed","breed_name", "sire"), 
                                strata = c("prod_system"), 
                                data= df, 
                                factorVars = c("prod_system"))

tableOne_anim
```


```{r}
tableOne_anim <- CreateTableOne(vars = c("birth_witness"), 
                                strata = c("birthlocation"), 
                                data= df, 
                                factorVars = c("birthlocation"))

tableOne_anim
```


```{r}
tableOne_anim <- CreateTableOne(vars = c("birthlocation","timeofbirth"), 
                                strata = c("typedelivery"), 
                                data= df, 
                                factorVars = c("typedelivery"))

tableOne_anim
```

Birth location by production system:
1. Mixed crop livestock
```{r}
df_mixed <- df[df$prod_system == "Mixed-crop", ]
df_mixed$prod_system <- factor(df_mixed$prod_system)

tableOne_anim <- CreateTableOne(vars = c("birthlocation"), 
                                strata = c("typedelivery"), 
                                data= df_mixed, 
                                factorVars = c("typedelivery"))

tableOne_anim
```


2. Pastoral
```{r}
df_pastoral <- df[df$prod_system == "Pastoral", ]
df_pastoral$prod_system <- factor(df_pastoral$prod_system)

tableOne_anim <- CreateTableOne(vars = c("birthlocation"), 
                                strata = c("typedelivery"), 
                                data= df_pastoral, 
                                factorVars = c("typedelivery"))

tableOne_anim
```


3. Peri-urban
```{r}
df_periurban <- df[df$prod_system == "Peri-urban", ]
df_periurban$prod_system <- factor(df_periurban$prod_system)

tableOne_anim <- CreateTableOne(vars = c("birthlocation"), 
                                strata = c("typedelivery"), 
                                data= df_periurban, 
                                factorVars = c("typedelivery"))

tableOne_anim
```


Time of birth:
1. Mixed crop livestock
```{r}
tableOne_anim <- CreateTableOne(vars = c("timeofbirth"), 
                                strata = c("typedelivery"), 
                                data= df_mixed, 
                                factorVars = c("typedelivery"))

tableOne_anim
```

2. Pastoral
```{r}
tableOne_anim <- CreateTableOne(vars = c("timeofbirth"), 
                                strata = c("typedelivery"), 
                                data= df_pastoral, 
                                factorVars = c("typedelivery"))

tableOne_anim
```


3. Peri-urban
```{r}
tableOne_anim <- CreateTableOne(vars = c("timeofbirth"), 
                                strata = c("typedelivery"), 
                                data= df_periurban, 
                                factorVars = c("typedelivery"))

tableOne_anim
```



Associations between sex, sire, type of delivery, and time of birth.
```{r}
tableOne_anim <- CreateTableOne(vars = c("sire","typedelivery","timeofbirth", "birthlocation"), 
                                strata = c("sex"), 
                                data= df, 
                                factorVars = c("sex"))

tableOne_anim
```




----------------------
DAM-LEVEL RISK FACTORS
----------------------


```{r}
setwd("/Users/gemavidal/Box Sync/Vet/Projects and Papers/2020 YSM USAID Final Report")
df = read.csv("df_dam_cleaned.csv", stringsAsFactors = TRUE)
```

```{r}
str(df)
```


```{r}
levels(df$dam_alive)[levels(df$dam_alive) == ""] <- NA
levels(df$dam_deathwithin2weeksparturition)[levels(df$dam_deathwithin2weeksparturition) == ""] <- NA
levels(df$dam_motheringinstinct)[levels(df$dam_motheringinstinct) == ""] <- NA
levels(df$dam_vaccines_type)[levels(df$dam_vaccines_type) == ""] <- NA
levels(df$dam_vaccines2monthsbeforedelivery)[levels(df$dam_vaccines2monthsbeforedelivery) == ""] <- NA
```

Drop unused levels
```{r}
df[c(4,6,8:10)] <- lapply(df[c(4,6,8:10)], factor)
```


Categorical variables
```{r}
tableOne_dam <- CreateTableOne(vars = c("dam_alive","dam_deathwithin2weeksparturition",
                                         "dam_motheringinstinct","dam_vaccines_type",
                                         "dam_vaccines2monthsbeforedelivery"), 
                                strata = c("prod_system"), 
                                data= df, 
                                factorVars = c("prod_system"))

tableOne_dam
```


Continuous variables
```{r}
tableOne_dam <- CreateTableOne(vars = c("parity","dam_milkyield_liters",
                                         "dam_ageparturition_years", "dam_bcs1to5"), 
                                strata = c("prod_system"), 
                                data= df, 
                                factorVars = c("prod_system"))

tableOne_dam
```


Questions:
- I would like to see those significant differences by parity, by milk yield, by age at parturition, and by BCS (plot a box plot to see the differences) by production system.
- Who are those with poor mothering instinct? do they make less milk? do they have lower BCS? are they lower parity cows?
- What is the association between parity and age at parturition? does it contain the same type of information?

```{r}
#tiff('[write name of file here].tiff', units = 'cm', width = 19, height = 10, res = 600)

p = ggplot(df, aes(x = parity, color = prod_system))
p = p + geom_density()
#p = p + geom_vline(df, aes(xintercept=grp.mean, color = prod_system), linetype = 'dashed')
p = p + ggtitle("Distribution of dam parity by production system")
p = p + labs(fill = "Production System") + guides(shape = FALSE)
p = p + theme(plot.title = element_text(size = 12, face = "bold", margin = margin(10, 0, 10, 0)))
p = p + ylab("Density") + xlab("Parity")
p + scale_fill_brewer(type = "qual", palette = "Set2")

#dev.off()
```


By parity and production system
```{r}
p = ggplot(df, aes(x = parity, color = prod_system))
p = p + geom_boxplot()
p = p + ggtitle("Distribution of dam parity by production system")
p = p + labs(fill = "Production System") + guides(shape = FALSE)
p = p + theme(plot.title = element_text(size = 12, face = "bold", margin = margin(10, 0, 10, 0)))
p = p + xlab("Parity")
p + scale_fill_brewer(type = "qual", palette = "Set2")
p
```


By age at parturtion and production system
```{r}
p = ggplot(df, aes(x = dam_ageparturition_years, color = prod_system))
p = p + geom_boxplot()
p = p + ggtitle("Distribution of dam age at parturition by production system")
p = p + labs(fill = "Production System") + guides(shape = FALSE)
p = p + theme(plot.title = element_text(size = 12, face = "bold", margin = margin(10, 0, 10, 0)))
p = p + xlab("Age at parturition (years)")
p + scale_fill_brewer(type = "qual", palette = "Set2")
p
```



By milk yield and production system
```{r}
p = ggplot(df, aes(x = dam_milkyield_liters, color = prod_system))
p = p + geom_boxplot()
p = p + ggtitle("Distribution of milk yield (liters) by production system")
p = p + labs(fill = "Production System") + guides(shape = FALSE)
p = p + theme(plot.title = element_text(size = 12, face = "bold", margin = margin(10, 0, 10, 0)))
p = p + xlab("Milk Yield (liters)")
p + scale_fill_brewer(type = "qual", palette = "Set2")
p
```


By BCS and production system
```{r}
p = ggplot(df, aes(x = dam_bcs1to5, color = prod_system))
p = p + geom_boxplot()
p = p + ggtitle("Distribution of body condition score (1 to 5) by production system")
p = p + labs(fill = "Production System") + guides(shape = FALSE)
p = p + theme(plot.title = element_text(size = 12, face = "bold", margin = margin(10, 0, 10, 0)))
p = p + xlab("Body Condition Score (BSC)")
p + scale_fill_brewer(type = "qual", palette = "Set2")
p
```


What is the association between age at parturition and parity?
```{r, fig.height = 5, fig.width = 10, echo = FALSE}
p = ggplot(df, aes(x = parity, y = dam_ageparturition_years))
p = p + geom_point() + geom_smooth()
p = p + facet_wrap(~ prod_system, scales = 'free_x', ncol = 3)
p = p + ggtitle("Relationship between parity and age at parturtion using locally estimated scatterplot smoothing (LOESS)")
p = p + theme(plot.title = element_text(size = 12, face = "bold", margin = margin(10, 0, 10, 0)))
p = p + xlab("Parity") + ylab("Age at parturition (years)")
p + scale_fill_brewer(type = "qual", palette = "Set2")
p
```


Who are those with poor mothering instinct? are those the younger ones?
```{r}
levels(df$dam_motheringinstinct)
```


```{r, fig.height = 8, fig.width = 10, echo = FALSE}
df$dam_motheringinstinct <- factor(df$dam_motheringinstinct)

p = ggplot(df, aes(x = dam_ageparturition_years, color = dam_motheringinstinct), na.rm = TRUE)
p = p + geom_boxplot()
#p = p + facet_wrap(~ prod_system, scales = 'free_x', ncol = 2)
p = p + facet_wrap(~ prod_system, ncol = 1)
p = p + ggtitle("Distribution dam age at parturition (years) by dam mothering instict and production system")
p = p + labs(fill = "Production System") + guides(shape = FALSE)
p = p + theme(plot.title = element_text(size = 12, face = "bold", margin = margin(10, 0, 10, 0)))
p = p + xlab("Age at parturition (years)")
p + scale_fill_brewer(type = "qual", palette = "Set2")
p
```

How can I get rid of the NaN? So far, what I've done so far hasn't worked
Try to do one plot per production system instead of the facet_wrap
```{r}
df_mixed <- df[df$prod_system == 'Mixed-crop',]
df_mixed$prod_system <- factor(df_mixed$prod_system)
#df$dam_motheringinstinct <- factor(df$dam_motheringinstinct)
levels(df_mixed$dam_motheringinstinct)
```


```{r, fig.height = 8, fig.width = 10, echo = FALSE}
p = ggplot(df_mixed, aes(x = dam_ageparturition_years, color = dam_motheringinstinct))
p = p + geom_boxplot()
#p = p + facet_wrap(~ prod_system, scales = 'free_x', ncol = 2)
#p = p + facet_wrap(~ prod_system, ncol = 1)
p = p + ggtitle("Distribution dam age at parturition (years) by dam mothering instict and production system")
p = p + labs(fill = "Production System") + guides(shape = FALSE)
p = p + theme(plot.title = element_text(size = 12, face = "bold", margin = margin(10, 0, 10, 0)))
p = p + xlab("Age at parturition (years)")
p + scale_fill_brewer(type = "qual", palette = "Set2")
p
```




```{r, fig.height = 8, fig.width = 10, echo = FALSE}
p = ggplot(df, aes(x = dam_bcs1to5, color = dam_motheringinstinct), na.rm = TRUE)
p = p + geom_boxplot()
#p = p + facet_wrap(~ prod_system, scales = 'free_x', ncol = 2)
p = p + facet_wrap(~ prod_system, ncol = 1)
p = p + ggtitle("Distribution of body condition score (1 to 5) by mothering instinct and production system")
p = p + labs(fill = "Production System") + guides(shape = FALSE)
p = p + theme(plot.title = element_text(size = 12, face = "bold", margin = margin(10, 0, 10, 0)))
p = p + xlab("Body Condition Score (1 to 5)")
p + scale_fill_brewer(type = "qual", palette = "Set2")
p
```


```{r, fig.height = 8, fig.width = 10, echo = FALSE}
p = ggplot(df, aes(x = dam_milkyield_liters, color = dam_motheringinstinct), na.rm = TRUE)
p = p + geom_boxplot()
#p = p + facet_wrap(~ prod_system, scales = 'free_x', ncol = 2)
p = p + facet_wrap(~ prod_system, ncol = 1)
p = p + ggtitle("Distribution of milk yield (liters) by mothering instinct and production system")
p = p + labs(fill = "Production System") + guides(shape = FALSE)
p = p + theme(plot.title = element_text(size = 12, face = "bold", margin = margin(10, 0, 10, 0)))
p = p + xlab("Milk Yield (liters)")
p + scale_fill_brewer(type = "qual", palette = "Set2")
p
```


```{r}
tableOne_dam <- CreateTableOne(vars = c("dam_bcs1to5","dam_ageparturition_years", "dam_milkyield_liters"), 
                                strata = c("dam_motheringinstinct"), 
                                data= df, 
                                factorVars = c("dam_motheringinstinct"))

tableOne_dam
```


Association between BCS and milk yield.
```{r, fig.height = 5, fig.width = 10, echo = FALSE}
p = ggplot(df, aes(x = dam_bcs1to5, y = dam_milkyield_liters))
p = p + geom_point() + geom_smooth()
p = p + facet_wrap(~ prod_system, scales = 'free_x', ncol = 3)
p = p + ggtitle("Relationship between BCS and milk yield (lts.) using locally estimated scatterplot smoothing (LOESS)")
p = p + theme(plot.title = element_text(size = 12, face = "bold", margin = margin(10, 0, 10, 0)))
p = p + xlab("BCS (1 to 5)") + ylab("Milk yield (lts.)")
p + scale_fill_brewer(type = "qual", palette = "Set2")
p
```









